Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-20 documentation/paper.tex
Added high res grid search to paper
Fixed all the broken data!

This process was generalized to several other banding resolutions. Higher-resolution counterparts of $\beta_{8}$ included $\beta_{20}$ and $\beta_{40}$.

@@

In addition to the Fourier transform used in the original PICO-60 analysis, higher resolutions were computed by similar means. These included $\beta _{20}$ and $\beta _{40}$. Also, the full-resolution $\beta _{50,001}$ was input into a neural network directly, without any downscaling.

This time, position corrections were optionally applied to the input data, as they were the input to Acoustic Parameter. The resulting configurations are furthermore referred to as $FourierMLP(\beta_{N})$ and \\ $FourierMLP(PosCor(\beta_{N}, \chi))$. Several different resolutions $N$ of $\beta_{N}$ were used. While a variety of network architectures were tested, most had a small number of layers (on the order of three), applied dropout and L2 regularization, and used batch normalization once again.

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}. Increasing the number of bands to 20 did not improve the results; accuracy only reached 95\%, with an increased mean standard deviation of 0.42. Using 40 bands reduced the accuracy once again, to 91\%.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Neural networks trained on Fourier transforms.} \label{fft_wall_cuts}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Acc & Prec & Recall & CWSD \\
            \hline
            $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 96\% & 98\% & 97\% & 0.42 \\
            % ../experimental_data/validation_results/2018_07_16_banded_frequency_validation_passing_weighted_3_times.json
            \hline
            $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 100\% & 98\% & 0.29 \\
            % ../experimental_data/validation_results/2018_07_17_banded_frequency_not_position_corrected/banded_low_resolution_time1531831056_epoch249.json
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 100\% & 92\% & 0.44 \\
            % ../experimental_data/validation_results/2018_07_17_banded_frequency_not_position_corrected_with_position_input/banded_low_resolution_time1531837503_epoch18.json
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 98\% & 98\% & 0.43 \\
            % ../experimental_data/validation_results/2018_07_18_banded_frequency_25\%_dropout/banded_low_resolution_time1531922044_epoch154.json
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 99\% & 92\% & 0.54 \\
            % ../experimental_data/validation_results/2018_07_20_20_bands/high_resolution_frequency_time1532105605_epoch90.json
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 99\% & 93\% & 0.52 \\
            % ../experimental_data/validation_results/2018_07_20_20_bands_no_regularization/high_resolution_frequency_time1532113464_epoch172.json
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 0 & 0 & 3 & 91\% & 98\% & 90\% & 0.57 \\
            % ../experimental_data/validation_results/2018_07_20_40_bands/high_resolution_frequency_time1532107386_epoch101.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.0003 & 0 & 4 & 91\% & 94\% & 93\% & 0.53 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0_l2_lambda0.0003_hidden_layers3_time1533922958_epoch133.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.25 & 4 & 91\% & 96\% & 89\% & 0.56 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0.25_l2_lambda0.001_hidden_layers3_time1533924257_epoch115.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.5 & 3 & 89\% & 91\% & 91\% & 0.64 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0.5_l2_lambda0.001_hidden_layers2_time1533925299_epoch169.json
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 4 & 89\% & 90\% & 93\% & 0.65 \\
            % ../experimental_data/validation_results/2018_08_10_high_resolution_grid_search_with_wall_cuts/high_res_grid_search_dropout0.5_l2_lambda0.01_hidden_layers3_time1533925799_epoch91.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

It is very clear in Table \ref{fft_wall_cuts} that higher resolutions do not improve accuracy. Regularization, both dropout and L2, appears to have relatively little effect.

>>>>

@@

In addition to the banded Fourier transform $\beta_{8}$ used in the original PICO-60 analysis, the full-resolution $\beta _{50,001}$ was input into a neural network directly, without any downscaling.

When $\beta_{8}$ was used as input, position corrections were optionally applied to the input data, as they were the input to Acoustic Parameter. The resulting configurations are furthermore referred to as $FourierMLP(\beta_{N})$ and \\ $FourierMLP(PosCor(\beta_{N}, \chi))$. While a variety of network architectures were tested, most had a small number of layers (on the order of three), applied dropout and L2 regularization, and used batch normalization once again.

@@

It became evident very quickly that a high resolution was not required to get a high accuracy relative to the ground truth data. $FourierMLP(\beta_{8})$ managed an excellent 98\% validation accuracy, and also produced a mean class-wise standard deviation of 0.29. Its very decisive prediction distribution can be observed in Figure \ref{banded_no_pos_input_hist}.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Neural networks trained on Fourier transforms.} \label{fft_wall_cuts}
        \begin{tabular}{|l|l|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Acc & Prec & Recall & CWSD \\
            \hline
            $FourierMLP(PosCor(\beta_{8}, \chi))$ & 0 & 0.5 & 2 & 96\% & 98\% & 97\% & 0.42 \\
            % ../experimental_data/validation_results/2018_07_16_banded_frequency_validation_passing_weighted_3_times.json
            \hline
            $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 100\% & 98\% & 0.29 \\
            % ../experimental_data/validation_results/2018_07_17_banded_frequency_not_position_corrected/banded_low_resolution_time1531831056_epoch249.json
            \hline
            $FourierMLP(\beta_{50,001})$ & 0 & 0 & 2 & 95\% & 94\% & 98\% & 0.47 \\
            % ../experimental_data/validation_results/2018_10_20_high_resolution_grid_search_without_position_input//dropout0/l2_lambda0/hidden_layers1/time1540053737_epoch170.json
            \hline
            $FourierMLP(\beta_{50,001})$ & 0.001 & 0 & 4 & 95\% & 95\% & 98\% & 0.46 \\
            % ../experimental_data/validation_results/2018_10_20_high_resolution_grid_search_without_position_input/dropout0/l2_lambda0.001/hidden_layers3/time1540054370_epoch174.json
            \hline
            $FourierMLP(\beta_{50,001})$ & 0.001 & 0.5 & 4 & 94\% & 93\% & 98\% & 0.54 \\
            % ../experimental_data/validation_results/2018_10_20_high_resolution_grid_search_without_position_input/dropout0.5/l2_lambda0.001/hidden_layers3/time1540056735_epoch50.json
            \hline
            $FourierMLP(\beta_{50,001})$ & 0.003 & 0.25 & 3 & 93\% & 92\% & 98\% & 0.57 \\
            % ../experimental_data/validation_results/2018_10_20_high_resolution_grid_search_without_position_input/dropout0.25/l2_lambda0.003/hidden_layers2/time1540055639_epoch113.json
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

It is very clear in Table \ref{fft_wall_cuts} that higher resolution data does not improve accuracy. Regularization, both dropout and L2, appears to have relatively little effect.
